Solution of Differential Algebraic Equations with Manifold Constraints on the Latent Space of an Autoencoder

### 2019-06-15 paper/paper.tex
New citations

% {\bf RESERVOIR PHYSICS LIT REVIEW HERE; Other applications;
% plasticity, }
One of the simulators with the widest-encompassing physical modules is
the TOUGH family of solvers that have been developed at Lawrence
Berkeley National Lab.
The methodology is based on a primary variable switching method in 
The simulator of THAT GUY WITH DUAL VARIABLES I MET AT AGU
parameterizes a simplified hydrate system using density and enthalpy
as the primary variables.
Higher order representations of flow are also a problem to tackle
anisotropy and increase the computational efficiency of the spatial
discretization. CITE ME AND MICKEY AND STEPHAN
Multiphase flow was done with finite elements in \cite{YANG2014417}.
THAT MORIDIS FEM PAPER
However, the complexity of the state representation restricts
development to a 2-phase

@@

 A program synthesis approach was used to search for and evaluate possible methods of Peridynamics in Queiruga, 2017 \cite{queiruga2017numerical}. (An open source implementation of the study can be found Periflakes\cite{queiruga2018periflakes}.)

@@

There are many ways to solve this cannonical equation: Lagrange
multipliers (\(f(t)\) is the multiplier in the way we have written it
above), penalties, change of variables, etc. The change of variables
method exploits the Lagrangian mechanics formulation, where we state
the Lagrangian,
\begin{equation}
L = \frac{1}{2}m\left(\dot{x}^2 + \dot{y}^2\right) - m g y
\end{equation}
with the constraint that \(x\) and \(y\) lie on the path.
We can introduce a new variable \(\theta\) that parameterizes
\(x=R\cos\theta\) and \(y=R\sin\theta\) and rederive the equations of
motion with the familiar,
\begin{align}
\text{Solve for}\, \theta(t) \ \text{satisfying:} \\
\frac{\mathrm{d}}{\mathrm{d}t} \frac{\partial L}{\partial
  \dot{\theta}} =
  \frac{\partial L}{\partial \theta}
\end{align}
In this example, this lets us collapse the problem into a
single-component second-roder differential equation.

>>>>

% {\bf RESERVOIR PHYSICS LIT REVIEW HERE; Other applications;
% plasticity, }
One of the simulators with the widest-encompassing physical modules is
the TOUGH family of solvers that have been developed at Lawrence
Berkeley National Lab.
The methodology is based on a primary variable switching method in 
The simulator of THAT GUY WITH DUAL VARIABLES I MET AT AGU
parameterizes a simplified hydrate system using density and enthalpy
as the primary variables.
Higher order representations of flow are also a problem to tackle
anisotropy and increase the computational efficiency of the spatial
discretization\cite{hannon_enhanced_2018}. 
Multiphase flow was done with finite elements in \cite{yang_fully_2014}.
THAT MORIDIS FEM PAPER
However, the complexity of the state representation restricts
development to a 2-phase

@@

 A program synthesis approach was used to search for and evaluate
 possible methods of Peridynamics in Queiruga, 2017
 \cite{queiruga_numerical_2017}. (An open source implementation of the
 study can be found Periflakes\cite{queiruga_periflakes_2019} using the
 Popcorn/Cornflakes system for symbolic code generation
 \cite{queiruga_cornflakes:_2018,queiruga_popcorn:_2018}.)

@@

There are many ways to solve this canonical equation: Lagrange
multipliers (\(f(t)\) is the multiplier in the way we have written it
above), penalties, change of variables, etc. The change of variables
method exploits the Lagrangian mechanics formulation, where we state
the Lagrangian,
\begin{equation}
L = \frac{1}{2}m\left(\dot{x}^2 + \dot{y}^2\right) - m g y
\end{equation}
with the constraint that \(x\) and \(y\) lie on the path.
We can introduce a new variable \(\theta\) that parameterizes
\(x=R\cos\theta\) and \(y=R\sin\theta\) and rederive the equations of
motion with the familiar,
\begin{align}
\text{Solve for}\, \theta(t) \ \text{satisfying:} \\
\frac{\mathrm{d}}{\mathrm{d}t} \frac{\partial L}{\partial
  \dot{\theta}} =
  \frac{\partial L}{\partial \theta}
\end{align}
In this example, this lets us collapse the problem into a
single-component second-roder differential equation.
